### 2010-10-13 papers/BMD2010/PhysicalParametersPaper/paper.tex
about to delete the mini tables
taking a break

\begin{table}
	\begin{tabular}{llllllll}
	Bicycle   & B      & B*     & C      & G      & P      & S      & Y \& Y*\\
    \hline
	Front\\
    \hline
    $p_\mathrm{F}$ [bar] & 3.5    & 3.5    & 4      & 4      & 6.9    & 4.5    & 4      \\
    $d_\mathrm{F}$ [m]   & 28.060 & 27.980 & 27.980 & 29.044 & 29.366 & 27.772 & 27.925 \\
    $n_\mathrm{F}$ []    & 13     & 13     & 13     & 14     & 14     & 13     & 13     \\
    \hline
	Rear\\
    \hline
	$p_\mathrm{R}$ [bar] & 3.5    & 3.5    & 4      & 4      & 6.9    & 4.5    & 3.5    \\
	$d_\mathrm{R}$       & 27.850 & 27.835 & 27.768 & 29.788 & 29.212 & 29.774 & 27.884 \\
	$n_\mathrm{R}$ []    & 13     & 13     & 13     & 14     & 14     & 14     & 13     \\
	\end{tabular}
	\caption{Raw data for the wheel radius measurements.}
	\label{tab:wheelRadius}
\end{table}

@@

\begin{table}
	\begin{tabular}{lllllllll}
    \hline
	Bicycle   & B      & B*     & C      & G      & P      & S      & Y      & Y*\\
	Head tube angle & 67.1 & 67.1 & 69.0 & 71.1 & 74.2 & 73.1 & 72.7 & 70.6\\
	Steer axis tilt & 0.400 & 0.400 & 0.367 & 0.330 & 0.276 & 0.295 & 0.302 & 0.339
	\end{tabular}
	\caption{Head tube angle and steer axis tilt}
	\label{tab:lambda}
\end{table}

\subsection{Trail}
Trail is difficult to measure directly so we instead chose to measure the fork
offset. The fork offset was measured by clamping the steer tube of the front
fork into a v-block on a flat table. A ruler was used to measure the height of
the center of the head tube and the height of the center of the axle axis. The
fork blades where aligned such that the axle axis was parallel to the table
surface.
\begin{equation}
	c=\frac{r_\mathrm{F}\sin{\lambda}-f_o}{\cos{\lambda}}
	\label{eq:trail}
\end{equation}
\begin{equation}
    \sigma_{c}^{2}=\sigma_{r_{\mathrm{F}}}^{2}\tan^2{\lambda} -
    \sigma_{f_o}^{2}\sec^2{\lambda} +
    \sigma_{\lambda}^{2}\left(r_\mathrm{F}\sec^2{\lambda} -
    f_o\sec{\lambda}\tan{\lambda}\right)^2
    \label{eq:TrailVar}
\end{equation}
\begin{table}
	\begin{tabular}{lllllllll}
	Bicycle     & B     & B*    & C     & G     & P     & S     & Y     & Y*\\
    \hline
	Fork offset & 0.071 & 0.071 & 0.045 & 0.039 & 0.032 & 0.045 & 0.057 & -0.057\\
	Trail       & 0.069 & 0.068 & 0.083 & 0.072 & 0.062 & 0.056 & 0.047 & 0.180
	\end{tabular}
	\caption{Head tube angle and steer axis tilt}
	\label{tab:trail}
\end{table}
\subsection{Wheelbase}
The wheelbase was measured directly using a tape measure while the bicycle was
in the same upright fixed position used when measuring the head tube angle.
\begin{table}
	\begin{tabular}{lllllllll}
	Bicycle    & B     & B*    & C     & G     & P     & S     & Y     & Y*\\
    \hline
	Wheel base & 1.121 & 1.121 & 1.101 & 1.070 & 0.989 & 1.037 & 1.089 & 0.985
	\end{tabular}
	\caption{Wheelbase values.}
	\label{tab:wheelbase}
\end{table}

@@

        \includegraphics[width=4in]{../../../images/massScale.jpg}

@@

\begin{table}
	\begin{tabular}{llllllllll}
		Bicycle &     $\sigma_m$ & B     & B*    & C     & G     & P    & S     & Y     & Y*\\
        \hline
		total   &    0.1       & 18.5  & 23.5  & 20.9  & 10.5  & 9.9  & 17.6  & 10.2  & 10.2\\
        \hline
		frame   &    0.02      & 9.86  & 14.71 & 9.18  & 4.48  & 4.49 & 7.22  & 3.31  & 3.31\\
		fork    &    0.02      & 3.22  & 3.22  & 4.57  & 2.52  & 2.27 & 3.04  & 2.45  & 2.45\\
		rear wheel & 0.02      & 3.11  & 3.11  & 3.96  & 1.94  & 1.38 & 3.96  & 2.57  & 2.57\\
		front wheel& 0.02      & 2.02  & 2.02  & 3.55  & 1.50  & 1.58 & 3.33  & 1.90  & 1.90\\
		total sum  & 0.04      & 18.21 & 23.06 & 21.26 & 10.44 & 9.72 & 17.55 & 10.23 & 10.23
	\end{tabular}
	\caption{Mass of bicycles and parts}
	\label{tab:mass}
\end{table}

@@

        \includegraphics[width=4in]{../../../images/pendDist.jpg}

@@

\subsection{Fork}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/StratosForkTorsionalThird.jpg}
    \end{center}
    \caption{The Stratos fork and handlebar assembly hung as a torsional
    pendulum.}
    \label{fig:StratosFork}
\end{figure}
\section{Parameters}
\section{Linear Analysis}
\subsection{Canonical Matrices}
The final results are presented in the form used by the benchmark model. These
can be used to populate the canonical form
\begin{equation}
\mathbf{M\ddot{q}}+v\mathbf{C}_1\mathbf{\dot{q}}+\left[g\mathbf{K}_0+v^2\mathbf{K}_2\right]\mathbf{q}=0
\label{eq:canonical}
\end{equation}
of the linear benchmark equations of motion presented in
\cite{Meijaard2007}. The coefficient matrices for the
example rider and bicycle follow in Eqs.~\ref{eq:M}-\ref{eq:K2}.
\subsection{Eigenvalues}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../plots/Bike/CrescendoRootLoci.png}
    \end{center}
    \caption{The root loci with speed as the parameter for the Crescendo.}
    \label{fig:StratosFork}
\end{figure}

>>>>

@@

\subsection{TRAIL}
Trail is difficult to measure directly so we instead chose to measure the fork
offset. The fork offset was measured by clamping the steer tube of the front
fork into a v-block on a flat table. A ruler was used to measure the height of
the center of the head tube and the height of the center of the axle axis. The
fork blades where aligned such that the axle axis was parallel to the table
surface.
	c=\frac{r_\mathrm{F}\sin{\lambda}-f_o}{\cos{\lambda}}
	\label{eq:trail}
    \sigma_{c}^{2}=\sigma_{r_{\mathrm{F}}}^{2}\tan^2{\lambda} -
    \sigma_{f_o}^{2}\sec^2{\lambda} +
    \sigma_{\lambda}^{2}\left(r_\mathrm{F}\sec^2{\lambda} -
    f_o\sec{\lambda}\tan{\lambda}\right)^2
    \label{eq:TrailVar}
\subsection{Wheelbase}
The wheelbase was measured directly using a tape measure while the bicycle was
in the same upright fixed position used when measuring the head tube angle.

@@

        \includegraphics[width=3in]{../../../images/massScale.jpg}

@@

@@

        \includegraphics[width=3in]{../../../images/pendDist.jpg}

@@

\subsection{Fork}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../images/StratosForkTorsionalThird.jpg}
    \end{center}
    \caption{The Stratos fork and handlebar assembly hung as a torsional
    pendulum.}
    \label{fig:StratosFork}
\end{figure}
\section{Parameters}
\section{Linear Analysis}
\subsection{Canonical Matrices}
The final results are presented in the form used by the benchmark model. These
can be used to populate the canonical form
of the linear benchmark equations of motion presented in
\cite{Meijaard2007}.
\subsection{Eigenvalues}
\begin{figure}[htbp]
    \begin{center}
        \includegraphics[width=4in]{../../../plots/Bike/CrescendoRootLoci.png}
    \end{center}
    \caption{The root loci with speed as the parameter for the Crescendo.}
    \label{fig:rootloci}
\end{figure}
